Optimal Particle Paths Around Points in $\R^2$ with Constrained Acceleration

### 2013-10-07 path_theorems.tex
Compiled paper (no more conflicts).
Changing path theorems.

\begin{theorem}
  Given a particle $p \in \mathrm{R}^2$ whose initial position is $\bvec{X_1}$ and moves with bounded tangential acceleration, $a_t \le \bar{a}_{t}$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $\bvec{X_1}$ to $\bvec{X_2}$ lies on the line segment from $\bvec{X_1}$ to $\bvec{X_2}$:
\end{theorem}

@@

\begin{corollary}
  Given points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ and a particle $p$ whose initial position is $(x_1, y_1)$ which moves with acceleration bounded by $\bar{a}$, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $(x_1, y_1)$ to $(x_2, y_2)$ is unique.
\end{corollary}
\proof We have already shown that any fastest path between $(x_1, y_1)$ and $(x_2, y_2)$ follows the straight line given by $y = \frac{y_2 - y_1}{x_2 - x_1} x + y_1$. Moreover, we showed that when travelling along the fastest path, the particle must have acceleration along the straight line of $\bar{a}$. Since we have starting position $(x_1, y_1)$ and initial speed of $0$, the acceleration of the particle $a(t)$ uniquely defines a path for the particle.

There is only a single function $a(t) = \bar{a}$ which the acceleration can satisfy when the particle is moving along a fastest path, therefore, there is only a single possible fastest path.
\qed

@@

\begin{conjecture}
  Let particles $p_1, p_2$ have initial velocities $\bvec{v}_1, \bvec{v}_2$ and starting positions $\bvec{x}_1 = \bvec{x}_2$ respectively. Additionally, let $p_1, p_2$ have constant speed conditions and let the end position be $\bvec{x}_f$ such that $d(\bvec{x}_f, \bvec{x}_1) = d(\bvec{x}_f, \bvec{x}_2) > R_{min}$. If $d(\bvec{x}_1, \bvec{x}_f) \leq d(\bvec{x}_2, \bvec{x}_f)$ and $\theta_{p_1}(T_0) < \theta_{p_2}(T_0)$, then $T_f(\bhat{\gamma_1}) < T_f(\bhat{\gamma_2})$.
\end{conjecture}

@@

\begin{corollary}
  Given conditions set forth in theorem \ref{theorem:restricted-theta}, we have:
  \begin{eqnarray}
    T_f(\bhat{\gamma_p}}) = v_0 \left( \left( \pi - \arccos \frac{R_{min}}{d - R_{min}} \right) 2 \pi R_{min}  + \sqrt{d^2 - 2 R_{min} d}  \right)
  \end{eqnarray}
\end{corollary}

>>>>

\begin{theorem}
  \label{theorem:line-proof}
  Given a particle $p \in \mathrm{R}^2$ with initial position of $\bvec{X_1}$, no initial speed, and moves with bounded tangential acceleration, $a_t \le \bar{a}_{t}$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $\bvec{X_1}$ to $\bvec{X_2}$ lies on the line segment from $\bvec{X_1}$ to $\bvec{X_2}$:
\end{theorem}

@@

\begin{corollary}
  Given points $\bvec{X_1}, \bvec{X_f} \in \mathrm{R}^2$ and a particle $p$ whose initial position is $\bvec{X_1}$ which moves under conditions set forth in \ref{theorem:line-proof}, the fastest path $\hat{\gamma}(t)$ which $p$ can trace to $\bvec{X_f}$ is unique.
\end{corollary}
\proof We have already shown that any fastest path between $\bvec{X_1}$ and $\bvec{X_f}$ follows the straight line between them. Moreover, we showed that when travelling along the fastest path, the particle must have tangential acceleration of $\bar{a}_t$. Since we have starting position $\vec{X_1}$ and initial speed of $0$, the acceleration of the particle uniquely defines a path for the particle.

There is only a single function $a(t) = \bar{a}_t$ which the acceleration can satisfy when the particle is moving along a fastest path, therefore, there is only a single possible fastest path.
\qed

@@

\begin{conjecture}
  Let particles $p_1, p_2$ have initial velocities $\bvec{v}_1, \bvec{v}_2$ and starting positions $\bvec{x}_1, \bvec{x}_2$ respectively. Additionally, let $p_1, p_2$ have constant speed conditions and let the end position be $\bvec{x}_f$ such that $d(\bvec{x}_f, \bvec{x}_1) = d(\bvec{x}_f, \bvec{x}_2) > R_{min}$. If $d(\bvec{x}_1, \bvec{x}_f) \leq d(\bvec{x}_2, \bvec{x}_f)$ and $\theta_{p_1}(T_0) < \theta_{p_2}(T_0)$, then $T_f(\bhat{\gamma_1}) < T_f(\bhat{\gamma_2})$.
\end{conjecture}

@@

\begin{corollary}
  Given conditions set forth in theorem \ref{theorem:restricted-theta}, we have:
  \begin{eqnarray}
    T_f(\bhat{\gamma_p}) = v_0 \left( \left( \pi - \arccos \frac{R_{min}}{d - R_{min}} \right) 2 \pi R_{min}  + \sqrt{d^2 - 2 R_{min} d}  \right)
  \end{eqnarray}
\end{corollary}
